\begin{description}
  \item[Algorithm:] step-by-step set of operations to be performed.
  \item[Crawler:] programmable machine / piece of software that receives input, stores and manipulates data, and provides output in a useful format.
  \item[Data structure:] Is a particular way of storing and organising data in a computer so that it can be used efficiently.
  \item[DOM:] The XML DOM defines a standard way for accessing and manipulating XML documents. The DOM presents an XML document as a tree-structure. 
  \item[Dow Jones:] Is a stock market index.
  \item[Framework:] Universal and reusable software environment that provides particular functionality as part of a larger software platform to facilitate development of software applications, products and solutions.
  \item[GATE:] A computer architecture for a broad range of Natural Language Processing tasks, available under the GNU Public License.
  \item[Hash tables:] Data structure used to implement an associative array, a structure that can map keys to values.
  \item[HTML:] HyperText Markup Language is the standard markup language used to create Web pages.
  \item[Http:] Hypertext Transfer Protocol (HTTP) is an application protocol for distributed, collaborative, hypermedia information systems. Is the foundation of the World Wide Web.
  \item[JSOUP:] Java library for working with real-world HTML. It provides a very convenient API for extracting and manipulating data, using the best of DOM, CSS, and jquery-like methods Web page: http://jsouporg/
  \item[Lexemes:] Unit of lexical meaning that exists regardless of the number of inflectional endings it may have or the number of words it may contain.
  \item[Lexicon:] Language's inventory of lexemes.
  \item[News endpoint:] Entry point where news articles are published from several authors.
  \item[NYSE:] New York Stock Exchange
  \item[Query string:] Part of a uniform resource locator that contains data to be passed by web applications.
  \item[RSS:] Family of standard web feed formats to publish frequently updated information: blog entries, news headlines, audio, video.
  \item[S&P 500:] American stock market index based on the market capitalisation of 500 large companies having common stock listed on the NYSE or NASDAQ
  \item[Sentiment analysis:] Use of natural language processing, text analysis and computational linguistics to identify and extract subjective information in source materials
  \item[Stemming:] The process for reducing inflected (or derived) words to their word stem
  \item[Stock market index:] Measurement of the value of a section of the stock market It is computed from the prices of selected stocks It is a tool used by investors and financial managers to describe the market, and to compare the return on specific investments
  \item[Text mining:] Process of deriving high-quality/structured information from text/unstructured information
  \item[Tokenization:] Process of breaking a stream of text up into words, phrases, symbols, or other meaningful elements called tokens
  \item[Web API:] Acronym of "Web Application programming interface", which is defined as a request/response message system, which is exposed on the web.
  \item[WHATWG:] Web Hypertext Application Technology Working Group (WHATWG) is a community of people interested in evolving HTML and related technologies.
\end{description}